---
title: "RWorksheet_Nava#3b"
author: "Samantha Nicole Nava"
date: "2024-09-31"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
1.
a.
```{r}
library(readxl)
resdata <- read_excel("respondents_data.xlsx")
head(resdata)

```
b.
```{r}
str(resdata)
```
```{r}
summary(resdata)
```
c.
yes
d.
```{r}
firsttwo <- resdata[1:2, ]
firsttwo
```
e.
```{r}
selected <- resdata[c(3, 5), c(2, 4)]
selected
```
f.
```{r}
types_houses <- resdata$`Types of houses`
types_houses
```
g.
```{r}
male_farmers <- resdata[resdata$Sex == 1 & resdata$`Fathers Occupation` == 1, ]
male_farmers
```
h.
```{r}
females_with_siblings <- resdata[resdata$Sex == 2 & resdata$`Siblings at school` >= 5, ]
females_with_siblings
```
2.
```{r}
df = data.frame(Ints=integer(),
Doubles=double(), Characters=character(), Logicals=logical(),
Factors=factor(), stringsAsFactors=FALSE)
print("Structure of the empty dataframe:")
```
```{r}
print(str(df))
```
a.
The dataframe is empty but it has 5 columns of different types.
3.
a.
```{r}
respondents_data <- read.csv("respondents_data.csv")
respondents_data
```
b.
```{r}
respondents_data$Sex <- factor(respondents_data$Sex, levels = c("Male", "Female"), labels = c(1, 2))
respondents_data$Sex
```
c.
```{r}
respondents_data$Types.of.Houses <- factor(respondents_data$Types.of.Houses, levels = c("Wood", "Concrete", "Semi-concrete"), labels = c(1, 2, 3))
respondents_data$Types.of.Houses
```
d.
```{r}
respondents_data$Fathers.Occupation <- factor(respondents_data$Fathers.Occupation, levels = c(1, 2, 3), labels = c("Farmer", "Driver", "Others"))
respondents_data$Fathers.Occupation <- as.integer(respondents_data$Fathers.Occupation)
respondents_data$Fathers
```
e.
```{r}
respondents_data$Fathers.Occupation <- factor(respondents_data$Fathers.Occupation, levels = c(1, 2, 3), labels = c("Farmer", "Driver", "Others"))
respondents_data$Fathers.Occupation <- as.integer(respondents_data$Fathers.Occupation)
respondents_data$Fathers
```
f.
```{r}
siblings5 <- respondents_data[respondents_data$Siblings.at.School >= 5, ]
siblings5
```
4.
The graph plots the daily sentiment of the tweets, categorized by color to represent different tweet types. It can be seen that there is a persistent pattern where negative tweets are always greater than neutral or positive tweets. That means Twitter is primarily used to voice critical opinions or negativity.
