---
title: "RWorksheet_Nava#4a"
author: "Samantha Nicole Nava"
date: "2024-10-14"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
1. The table below shows the data about shoe size and height.
```{r}
library(openxlsx)
Household_Data <- read.xlsx("household_data2.xlsx")
Household_Data
```
a. The data shows the gender, height and shoe size.
b.
Male subset and Female subset
```{r}
male_data <- subset(Household_Data, Gender == "M") 
female_data <- subset(Household_Data, Gender == "F")
male_data
female_data
```
c.
```{r}
mean_shoesize <- mean(Household_Data$`Shoe Size`)
mean_shoesize

mean_height <- mean(Household_Data$Height)
mean_height
```
d. Is there a relationship between shoe size and height? Why?
Yes. There is a relationship between shoe size and height. I noticed that those who have taller height have bigger shoe size.

FACTORS
2.
Construct character vector months to a factor with factor() and assign the result to
factor_months_vector. Print out factor_months_vector and assert that R prints out
the factor levels below the actual values.
```{r}
months_vector <- c("March", "April", "January", "November", "January",
                   "September", "October", "September", "November", "August",
                   "January", "November", "November", "February", "May", "August",
                   "July", "December", "August", "August", "September", "November",
                   "February", "April")

```

```{r}
factor_months_vector <- factor(months_vector)
```
3.
Then check the summary() of the months_vector and factor_months_vector. | Inter-
pret the results of both vectors. Are they both equally useful in this case?

```{r}
summary_months_vector <- summary(months_vector)
summary_factor_months_vector <- summary(factor_months_vector)

summary_months_vector
summary_factor_months_vector
```
In this case, the factor vector is helpful. It has straightforward, organized information, whereas the character vector requires processing in order to extract similar information from it.

4.
```{r}
direction <- c("East", "West", "North")
frequency <- c(1, 4, 3)
```
```{r}
factor_data <- factor(direction, levels = c("East", "West", "North"))
```
```{r}
new_order_data <- factor(factor_data, levels = c("East", "West", "North"))
new_order_data
```
5.
```{r}
library(openxlsx)
data <- read.table("student.csv", header = TRUE, sep = ",", stringsAsFactors = TRUE)

```
```{r}
print(head(data))
```
6.
Create an R Program that allows the User to randomly select numbers from 1 to 50.
Then display the chosen number. If the number is beyond the range of the selected choice,
it will have to display a string “The number selected is beyond the range of 1 to 50”. If
number 20 is inputted by the User, it will have to display “TRUE”, otherwise display the
input number.
```{r}
num <- readline(prompt="Enter a number from 1-50")
num 

if (num>50){
  print("The number selected is beyond the range of 1 to 50")
} else if (num==20){
  print("TRUE")
} else {
  num
}
```
7. Change
a.
```{r}
minBills <- function(price){
  
  bills <- c(1000, 500, 200 , 100 ,50)
  
  billCount <- 0
  
  billCount <- billCount + price %/% bills[1]  
  price <- price %% bills[1]                    
  
  billCount <- billCount + price %/% bills[2]  
  price <- price %% bills[2]                     
  
  billCount <- billCount + price %/% bills[3]  
  price <- price %% bills[3]                     
  
  billCount <- billCount + price %/% bills[4]  
  price <- price %% bills[4]                     
  
  billCount <- billCount + price %/% bills[5] 
  price <- price %% bills[5]                     

  
  cat("Minimum number of bills needed:", billCount, "\n")
}

minBills(8000)  

```
8.
a.
```{r}
studentsScores <- data.frame(
  Name = c("Annie", "Thea", "Steve", "Hanna"),
  Grade1 = c(85, 65, 75, 95),
  Grade2 = c(65, 75, 55, 75),
  Grade3 = c(85, 90, 80, 100),
  Grade4 = c(100, 90, 85, 90)
)

(studentsScores)

```
b.
```{r}

total_scores <- studentsScores$Grade1 + studentsScores$Grade2 + studentsScores$Grade3 + studentsScores$Grade4


average_scores <- total_scores / 4

for (i in 1:nrow(studentsScores)) {
  if (average_scores[i] > 90) {
    cat(studentsScores$Name[i], "'s average grade this semester is", round(average_scores[i], 2), "(above 90).\n")
  } else if (average_scores[i] == 90) {
    cat(studentsScores$Name[i], "'s average grade this semester is", round(average_scores[i], 2), "(exactly 90).\n")
  }
}

```
c.
```{r}
num_students <- nrow(studentsScores)


total_scores <- c(0, 0, 0, 0)


for (i in 1:num_students) {
  total_scores[1] <- total_scores[1] + studentsScores$Grade1[i]  
  total_scores[2] <- total_scores[2] + studentsScores$Grade2[i]  
  total_scores[3] <- total_scores[3] + studentsScores$Grade3[i] 
  total_scores[4] <- total_scores[4] + studentsScores$Grade4[i] 
}

for (j in 1:length(total_scores)) {
  average_score <- total_scores[j] / num_students
  if (average_score < 80) {
    cat("Test", j, "was difficult.\n")
  }
}
```
d.
```{r}
highest_scores <- apply(studentsScores[2:5], 1, function(x) {
  highest_score <- x[1]  
  for (score in x) {
    if (score > highest_score) {
      highest_score <- score
    }
  }
  return(highest_score)
})


for (i in 1:nrow(studentsScores)) {
  if (highest_scores[i] > 90) {
    cat(studentsScores$Name[i], "'s highest grade this semester is", highest_scores[i], ".\n")
  }
}
```



