---
title: "RWorksheet_Nava#4a"
author: "Samantha Nicole Nava"
date: "2024-10-14"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
1. The table below shows the data about shoe size and height.
```{r}
Household_Data <- read_excel("household_data1.xlsx")
Household_Data
```
a. The data shows the gender, height and shoe size.
b.
Male subset and Female subset
```{r}
male_data <- subset(Household_Data, Gender == "M") 
female_data <- subset(Household_Data, Gender == "F")
male_data
female_data
```
c.
```{r}
mean_shoesize <- mean(Household_Data$`Shoe Size`)
mean_shoesize

mean_height <- mean(Household_Data$Height)
mean_height
```
d. Is there a relationship between shoe size and height? Why?
Yes. There is a relationship between shoe size and height. I noticed that those who have taller height have bigger shoe size.

FACTORS
2.
Construct character vector months to a factor with factor() and assign the result to
factor_months_vector. Print out factor_months_vector and assert that R prints out
the factor levels below the actual values.
```{r}
months_vector <- c("March", "April", "January", "November", "January",
                   "September", "October", "September", "November", "August",
                   "January", "November", "November", "February", "May", "August",
                   "July", "December", "August", "August", "September", "November",
                   "February", "April")

```

```{r}
factor_months_vector <- factor(months_vector)
```
3.
Then check the summary() of the months_vector and factor_months_vector. | Inter-
pret the results of both vectors. Are they both equally useful in this case?

```{r}
summary_months_vector <- summary(months_vector)
summary_factor_months_vector <- summary(factor_months_vector)

summary_months_vector
summary_factor_months_vector
```
In this case, the factor vector is helpful. It has straightforward, organized information, whereas the character vector requires processing in order to extract similar information from it.

4.
```{r}
direction <- c("East", "West", "North")
frequency <- c(1, 4, 3)
```
```{r}
factor_data <- factor(direction, levels = c("East", "West", "North"))
```
```{r}
new_order_data <- factor(factor_data, levels = c("East", "West", "North"))
new_order_data
```
5.
```{r}
data <- read.table("student.csv", header = TRUE, sep = ",", stringsAsFactors = TRUE)

```
```{r}
View(data)
```
6.
Create an R Program that allows the User to randomly select numbers from 1 to 50.
Then display the chosen number. If the number is beyond the range of the selected choice,
it will have to display a string “The number selected is beyond the range of 1 to 50”. If
number 20 is inputted by the User, it will have to display “TRUE”, otherwise display the
input number.
```{r}
num <- readline(prompt="Enter a number from 1-50")
num 

if (num>50){
  print("The number selected is beyond the range of 1 to 50")
} else if (num==20){
  print("TRUE")
} else {
  num
}
```
7. Change
a.
```{r}
minBills <- function(price){
  
  bills <-(1000,500,200,100,50)
  
  billCount <- 0
  
}
```



