---
title: "RWorksheet_Nava#4b"
author: "Samantha Nicole Nava"
date: "2024-10-28"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)


```
Using Loop Function
1.
```{r}
vectorA <- c(1, 2, 3, 4, 5)


matrixResult <- matrix(0, nrow = 5, ncol = 5)

for (i in 1:5) {
  for (j in 1:5) {
    
    matrixResult[i, j] <- abs(vectorA[i] - vectorA[j])
  }
}


print(matrixResult)
```
2.
```{r}
numRows <- 5

for (i in 1:numRows) {
  for (j in 1:i) {
    cat('"*"', " ") 
  }
  cat("\n")  
}
```
3.
```{r}

startNum <- 0  


if (is.na(startNum) || startNum < 0) {
  stop("Please enter a valid non-negative number.")
}


fib1 <- 0
fib2 <- 1


cat("Fibonacci sequence starting from", startNum, "up to 500:\n")
repeat {
  if (fib1 >= startNum) {
    cat(fib1, "\n") 
  } 
  nextFib <- fib1 + fib2
  fib1 <- fib2
  fib2 <- nextFib
  

  if (fib1 > 500) {
    break
  }
}

```
Using Basic Graphics (plot(),barplot(),pie(),hist())
4.
a.
```{r}
library(openxlsx)


dataset <- read.xlsx("household_data2.xlsx", sheet = 1)  


print(head(dataset))
print(str(dataset)) 

dataset$Gender <- as.character(dataset$Gender)  # Convert to character if needed

```
b.
```{r}

library(openxlsx)

dataset <- read.xlsx("household_data2.xlsx", sheet = 1)

print(head(dataset))


uniqueValues <- unique(dataset$Gender)
print(uniqueValues)

male_subset <- subset(dataset, Gender == "M")
female_subset <- subset(dataset, Gender == "F")

numMales <- nrow(male_subset)
numFemales <- nrow(female_subset)

cat("Number of observations in Male:", numMales, "\n")
cat("Number of observations in Female:", numFemales, "\n")

```
5.
```{r}
categories <- c("Food", "Electricity", "Savings", "Miscellaneous")
expenses <- c(60, 10, 5, 25)


percentages <- round((expenses / sum(expenses)) * 100)


labels <- paste(categories, percentages, "%", sep = " ")


colors <- c("lightblue", "lightgreen", "pink", "purple")

# Create the pie chart
pie(expenses, labels = labels, col = colors, main = "Monthly Income Expenses of Dela Cruz Family")
```
6.
a.
```{r}
data(iris)

str(iris)
```
b.
```{r}
means <- colMeans(iris[, 1:4])
means
```
c.
```{r}

species_count <- table(iris$Species)


labels <- paste(names(species_count), species_count)


colors <- c("yellow", "pink", "lightblue")


pie(species_count, labels = labels, col = colors, main = "Species Distribution in Iris Dataset")
```
d.
```{r}

setosa <- subset(iris, Species == "setosa")
versicolor <- subset(iris, Species == "versicolor")
virginica <- subset(iris, Species == "virginica")


lastSixSetosa <- tail(setosa, 6)
lastSixVersicolor <- tail(versicolor, 6)
lastSixVirginica <- tail(virginica, 6)


lastSixSetosa
lastSixVersicolor
lastSixVirginica
```
e.
```{r}

iris$Species <- as.factor(iris$Species)


plot(iris$Sepal.Length, iris$Sepal.Width, 
     col = iris$Species, pch = 19,
     xlab = "Sepal Length", 
     ylab = "Sepal Width",
     main = "Iris Dataset",
     sub = "Sepal Width and Length")

legend("topright", legend = levels(iris$Species), col = 1:3, pch = 19)
```
f.
The scatter plot is a display of the variation within the iris species for changes in sepal length and width. You can see there is clustering - where some species are very close to another, hence similar in measurement.
For example, setosa may typically be distinguished from the rest, say versicolor and virginica, with smallersepal length and width. This might also suggest that setosa may be somewhat different from the other two species, whose measures overlap.:
The means computed in b give a summary measure for each measurement, providing the mean central tendency of each characteristic for all of the species. In this case, the higher mean values in the versicolor and virginica species for the characteristics Petal.Length and Petal.Width indicate that these species have larger petals compared to setosa.

7.

```{r}
library(openxlsx)


alexa_data <- read.xlsx("alexa_file.xlsx")


print("Original Dataset:")
print(head(alexa_data))  # Show the first 6 rows


alexa_data$Variants <- gsub("^\\s+|\\s+$", "", alexa_data$Variants)  # Trim leading and trailing spaces
alexa_data$Variants <- gsub("\\s+", " ", alexa_data$Variants)  # Replace multiple spaces with a single space


alexa_data$Variants <- gsub("Black Dot", "BlackDot", alexa_data$Variants)
alexa_data$Variants <- gsub("Black Plus", "BlackPlus", alexa_data$Variants)
alexa_data$Variants <- gsub("Black Show", "BlackShow", alexa_data$Variants)
alexa_data$Variants <- gsub("Black Spot", "BlackSpot", alexa_data$Variants)
alexa_data$Variants <- gsub("White Dot", "WhiteDot", alexa_data$Variants)
alexa_data$Variants <- gsub("White Plus", "WhitePlus", alexa_data$Variants)
alexa_data$Variants <- gsub("White Show", "WhiteShow", alexa_data$Variants)
alexa_data$Variants <- gsub("White Spot", "WhiteSpot", alexa_data$Variants)

print("Cleaned Dataset Snippet:")
print(head(alexa_data)) 


write.xlsx(alexa_data, "cleaned_alexa_file.xlsx")



```
b.
```{r}
library(dplyr)

variationCounts <- alexa_data %>%
  count(Variants)


save(variationCounts, file = "variations.RData")


print("Variation Counts:")
print(variationCounts)
```
c.
```{r}
barplot(variationCounts$n, 
        names.arg = variationCounts$Variants, 
        col = rainbow(nrow(variationCounts)), 
        main = "Frequency of Alexa Variants", 
        xlab = "Variants", 
        ylab = "Count", 
        las = 2)  
```
d.
```{r}

# Step 5: Separate counts for black and white variations
blackVariations <- variationCounts[grep("Black", variationCounts$Variants), ]
whiteVariations <- variationCounts[grep("White", variationCounts$Variants), ]

# Barplot for Black Variants
barplot(blackVariations$n, 
        names.arg = blackVariations$Variants, 
        col = "black", 
        main = "Count of Black Variants",
        xlab = "Variants", 
        ylab = "Count")

# Barplot for White Variants
barplot(whiteVariations$n, 
        names.arg = whiteVariations$Variants, 
        col = "lightgrey", 
        main = "Count of White Variants",
        xlab = "Variants", 
        ylab = "Count")


```

