---
title: "RWorksheet_Nava#2"
author: "Samantha Nicole Nava"
date: "2024-09-27"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
1.
a.
```{r}
x  <- -5:5
x
```
The ':' operator in R generates a sequence of integers. Here, the code  -5:5  creates a sequence starting from -5 and ending at 5, with a step size of 1. The output is a vector containing 11 elements, each representing an integer in the sequence.
b.
```{r}
x <- 1:7
x
```
2.
```{r}
x <- seq(1,3, by=0.2)
x
```
The  seq()  function in R generates a sequence of numbers. In this case, the code  seq(1, 3, by=0.2)  creates a sequence starting from 1 and ending at 3, with a step size of 0.2. The output is a vector containing 11 elements, each representing a value in the sequence.
3.
a.
```{r}
ages <- c(34, 28, 22, 36, 27, 18, 52, 39, 42, 29, 35, 31, 27, 22, 37, 34, 19, 20, 57, 49, 50, 37, 46, 25, 17, 37, 43, 53, 41, 51, 35, 24, 33, 41, 53, 40, 18, 44, 38, 41, 48, 27, 39, 19, 30, 61, 54, 58, 26, 18)


ages[3]

```
b.
```{r}
ages[-c(4, 12)]
```
4.
a.
```{r}
x <- c("first" = 3, "second" = 0, "third" = 9)
x[c("first", "third")]
```
The output shows the names of the vector elements ("first", "second", "third") and the values of the elements named "first" (3) and "third" (9).

b.

first third 
    3     9 
5.
a.
```{r}
x <- -3:2
x[2] <- 0
x
```
b.

[1] -3  0 -1  0  1  2

6.
a.
```{r}
month <- c("Jan", "Feb", "Mar", "Apr", "May", "Jun")
price_per_liter <- c(52.50, 57.25, 60.00, 65.00, 74.25, 54.00)
purchase_quantity <- c(25, 30, 40, 50, 10, 45)
fuel_data <- data.frame(month, price_per_liter, purchase_quantity)
fuel_data
```
b.
```{r}
weighted.mean(price_per_liter, purchase_quantity)
```
7.
a.
```{r}
riverdata <- c(length(rivers), sum(rivers), mean(rivers), median(rivers), var(rivers), sd(rivers), min(rivers), max(rivers))
riverdata
```
b.

[1]    141.0000  83357.0000    591.1844    425.0000 243908.4086    493.8708
[7]    135.0000   3710.0000

c.
```{r}
data <- c(length(rivers), sum(rivers), mean(rivers), median(rivers), var(rivers), sd(rivers), min(rivers), max(rivers))
data
```
8.
a.
```{r}
celebrity <- data.frame(
  Power_Ranking = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 22, 23, 24, 25),
  Celebrity_Name = c("Tom Cruise", "Rolling Stones", "Oprah Winfrey", "U2", "Tiger Woods", "Steven Spielberg",  "Howard Stern", "50 Cent", "Cast of the Sopranos", "Dan Brown", "Bruce Springsteen",  "Donald Trump", "Muhammad Ali", "Paul McCartney", "George Lucas", "Elton John", 
"David Letterman", "Phil Mickelson", "J.K Rowling", "Bradd Pitt", "Peter Jackson","Dr. Phil McGraw", "Jay Lenon", "Celine Dion", "Kobe Bryant"),
  Pay = c(67, 90, 225, 110, 90, 332, 302, 41, 52, 88, 55, 44, 55, 40, 233, 34, 40, 47, 75, 39, 45, 32, 30, 33, 31)
)
celebrity
```
b.
```{r}
celebrity[celebrity$Celebrity_Name == "J.K Rowling", c("Power_Ranking", "Pay")] <- c(15, 90)
celebrity
```
c.
```{r}
rank_data <- read.csv("Power-Ranking.csv")
rank_data
```
d.
```{r}
ranks_subset <-rank_data[10:20, ]
save(ranks_subset, file = "Ranks.RData")
```
9.
a.
```{r}
library(openxlsx)
hotels_data <- read.xlsx("hotels-vienna.xlsx")
hotels_data
```
b.
```{r}
dim(hotels_data)
```
c.
```{r}
selected_data <- hotels_data[, c("country", "neighbourhood", "price", "stars", "accommodation_type", "rating")]
selected_data
```
d.
```{r}
save(selected_data, file = "new.RData")
load("new.RData")
head(selected_data)  
```
e.
```{r}
tail(selected_data)
```

10.
a.
```{r}
vegetables <- c("Tomato", "Cucumber", "Carrot", "Potato", "Spinach", "Broccoli", "Pepper", "Lettuce", "Cabbage", "Onion")
vegetables
length(vegetables)
```
b.
```{r}
vegetables <- c(vegetables, "Zucchini", "Eggplant")
vegetables
length(vegetables)
```
c.
```{r}
newveg <- append(vegetables, c("Beetroot", "Garlic", "Peas", "Pumpkin"), after=5)
newveg
length(newveg)
```
d.
```{r}
newrveg <- newveg[-c(5, 10, 15)]
newrveg
length(newrveg)
```



